\section*{Declaration on the use of generative AI}
\label{sec:ai-declaration}

This project made substantial use of generative artificial intelligence:
large language models of the Anthropic Claude family (the Opus and Fable
generations, 2026), operated through an agentic coding interface with
multi-agent orchestration, under my direction and subject to my review at
every stage. Their role spanned several parts of the work: discovering and
organising the related literature and assembling the bibliography; proposing
diagnostic and robustness strategies, analytical framings, and candidate
interpretations; scaffolding and drafting analysis and packaging code;
executing the pre-committed estimation pipeline to regenerate the deposited
artifacts; building the verification and reproducibility infrastructure of
the replication package; and drafting and revising targeted passages of the
manuscript. Throughout, I treated these tools as fallible research aids
rather than as sources of authority, and subjected their output to a
verification protocol commensurate with their documented failure modes.

The integrity of the results does not rest on trust in that assistance. The
research question, the locked specification, the identification and
inference strategy, the data sources and their construction, and every
modelling and interpretive decision are my own; the specification was locked
before the diagnostic phase. No reported quantity was estimated by a
language model. All estimates derive from my seeded, deterministic pipeline,
which the assistant executed only to regenerate the committed artifacts; the
regenerated output was verified identical to my originals at reporting
precision, and every in-text numerical macro is byte-matched by a
non-regression guard. Two points warrant note. First, the size shares in
Table~\ref{tab:sizeratio} reflect a change of denominator basis that I
decided and the assistant implemented: deterministic arithmetic over
author-verified industry constants, not estimation, isolated and verified to
move exactly those quantities, with the prior convention retained as an
alternative row. Second, quantities quoted from primary sources were
inserted only after verbatim checking against those sources. Correctness is
therefore established by reproduction rather than by provenance: a single
command re-derives every table and figure from the deposited data on a fresh
clone, the guard confirms that all reported numbers are unchanged after any
code change, and AI-assisted modifications were accepted only when the
guard, the test suite, and a byte-level comparison of independently
regenerated artifacts agreed that the scientific content was unchanged.

The characteristic failure mode of language-model assistance is text that is
fluent but unsupported, and it was treated accordingly. The verification
layer identified and removed several fabricated or mis-attributed citations,
reworded or cut statements that could not be traced to a primary source or
to a re-executable computation, and caught coding errors before they reached
the results; I report this as evidence that verification was both necessary
and applied. The build automation, verification apparatus, and
data-acquisition scripts of the replication package are likewise
substantially AI-authored under my direction and approved by me, and the
committed result files were regenerated under a pinned deterministic
environment. These models do not meet the criteria for authorship. I
reviewed and approved all content and assume sole responsibility for this
paper, including any remaining errors.
