\section{Tail Inference}
\label{app:inference}

\paragraph{Same-specification standard-error ratio.}
The case for bootstrap inference at the tail
(Section~\ref{sec:method-inference}) rests on a same-specification
comparison. We take the bootstrap standard error from the exact headline-spec
bootstrap and the kernel standard error from the same table, at
$\tau = 0.01$ (Table~\ref{tab:seratio}). The ratio ranges from
\SeRatioMin{} to \SeRatioMax{} across horizons. This compares like with like.
A cross-specification comparison would instead conflate the standard-error
gap with differences in scale, controls, and shock definition.

\begin{table}[t]
\centering
\caption{Kernel versus bootstrap standard errors, same specification,
$\tau = 0.01$.}
\label{tab:seratio}
\input{../paper/tables/tabA2_se_ratio}
\begin{minipage}{0.85\textwidth}
\vspace{2pt}
{\scriptsize \emph{Notes:} Bootstrap standard error from the
exact-specification bootstrap; kernel standard error from the main
table. Source: \texttt{se\_ratio\_nb07.csv}.}
\end{minipage}
\end{table}

\paragraph{Block-length sensitivity.}
The 24-hour block length of the moving-block bootstrap is the maximal
horizon, the natural choice for the overlap structure. Nothing in our results
turns on it. Table~\ref{tab:blocksens} reports the 80\%-power minimum
detectable effect for the paired one-percent asymmetry, the object that
drives the equivalence bound, at block lengths of 12, 24, 36, and 48
hours. The bound moves by less than a tenth of its value across the range.
By construction the 24-hour column reproduces the corresponding cells of the
main exceedance table exactly, a built-in cross-check that the two run on
identical machinery.

\begin{table}[t]
\centering
\caption{Block-length sensitivity of the equivalence bound (MDE at 80\%
power, $\Delta$ at $\alpha = 1\%$).}
\label{tab:blocksens}
\input{../paper/tables/tabA1_block_sensitivity}
\begin{minipage}{0.85\textwidth}
\vspace{2pt}
{\scriptsize \emph{Notes:} Per-period paired bootstrap, $1{,}000$
replications. The 24-hour column reproduces the main exceedance results.
Source: \texttt{block\_sensitivity.csv}.}
\end{minipage}
\end{table}